Temporal Semantics to Go: A Complete Run of the FraCaS Test Suite

### 2021-04-19 paper2020/paper_2021.tex
minor

\begin{multline*}
\constant {subsumption}_P :\\ [t_3,t_4] ⊆ [t_1,t_2] → P (t_1,t_2) → P (t_3,t_4)
\end{multline*}
This principle is used to reason about problem (314), below:

@@

Further cases to be included in an extended FraCaS future suite
involve examples where the interaction between different tenses needs
to be captured:

>>>>

\begin{multline*}
\constant {subsumption}_P :\\ [t_3,t_4] ⊆ [t_1,t_2] → P (t_1,t_2) → P (t_3,t_4)
\end{multline*}
This principle is used to reason about problem (314), below (note that ``Smith'' is used as a surname in the FraCaS and can take both feminine and masculine values):

@@

Further cases to be included in an extended FraCaS future suite
involve examples where the interaction between different tenses needs
to be captured:\footnote{While this work was completed, the work by \cite{vashishtha-etal-2020} was published. The authors present a five datasets to be used for the training of neural models' ability to capture temporal reasoning. It would be interesting to check the amount of data covered, most specifiaclly the level of fine-grainedness of temporal reasoning needed to capture those examples, as compared to what we have been discussing in this paper. We thank an anonymous reviewer for bringing this work to our attention.}
